---
title: "AS3-3: 美國的人口統計和就業資料"
author: "第 6 組"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---
組員： B035040052 林榮鏵 B056090039 楊禾馨 M064020056閻俞蓉 M064111003 洪筱涵 M074111035 劉志峰
```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

就業統計數據是政策制定者用來衡量經濟整體實力的最重要指標之一。在美國，政府使用現有人口調查（CPS）衡量失業率，該調查每月收集來自各種美國人的人口統計和就業信息。在本練習中，我們將使用講座中審查的主題以及一些使用2013年9月版的，具有全國代表性的數據集。數據集中的觀察結果代表2013年9月CPS中實際完成調查的人員，完整數據集有385個欄位，但在本練習中，我們將使用數據集CPSData.csv版本，它具有以下欄位：

+ `PeopleInHousehold`: 受訪者家庭中的人數。
+ `Region`: 受訪者居住的人口普查區域。
+ `State`: 受訪者居住的州。
+ `MetroAreaCode`: 都會區代碼，如受訪者不住都會區，則為NA；從代碼到都會區名稱的對應在`MetroAreaCodes.csv`中提供。
+ `Age`: 受訪者的年齡，以年為單位。 80代表80-84歲的人，85代表85歲及以上的人。
+ `Married`: 受訪者的婚姻狀況。
+ `Sex`: 受訪者的性別。
+ `Education`: 受訪者獲得的最高教育程度。
+ `Race`: 受訪者的種族。
+ `Hispanic`: 受訪者是否屬於西班牙裔。
+ `CountryOfBirthcode`: 識別受訪者出生國家的代碼。從代碼到國家名稱的映射在CountryCodes.csv文件中提供。
+ `Citizenship`: 受訪者的公民身份。
+ `EmploymentStatus`: 受訪者的就業狀況。
+ `Industry`: 受訪者的就業行業（僅在受僱的情況下可用）。

- - -

<br><br>

###  Section-1 Loading and Summarizing the Dataset
```{r}
#讀取CPS並安裝%>%方便後續作業，下載dplyr後記得要把它註記掉喔！以免每次讀取都跑出來亂～
CPS=read.csv("data/CPSData.csv")
#install.packages("dplyr") 就是在說它
library(dplyr)
```

__§ 1.1__ How many interviewees are in the dataset?
```{r}
#讀取資料庫的觀察值數量
nrow(CPS)
```
有131302個

__§ 1.2__ Among the interviewees with a value reported for the Industry variable, what is the most common industry of employment? Please enter the name exactly how you see it.
```{r}
#列出各產業別數量
table(CPS$Industry)
```
最多的是 Educational and health services


__§ 1.3__ Which state has the fewest interviewees?
```{r}
#先列出所有州的面試者數量，再點出最少者
which.min(sort(table(CPS$State)))
```
New Mexico的受面試者最少

Which state has the largest number of interviewees?
```{r}
#先列出所有州的面試者數量，再點出最多者
which.max(sort(table(CPS$State)))
```
California的受面試者最多

__§ 1.4__ What proportion of interviewees are citizens of the United States?
```{r}
#列出個別項目後，再進行比率計算
table(CPS$Citizenship)
(116639+ 7073)/131302
```
比率是0.9422

__§ 1.5__ For which races are there at least 250 interviewees in the CPS dataset of Hispanic ethnicity? (Select all that apply.) 

+ American Indian
+ Asian
+ cBlack
+ Multiracial
+ Pacific Islander
+ White

```{r}
#先找出表格後，再目視挑出250以上者
table(CPS$Hispanic,CPS$Race)
```
共4種：Indian, Black, Multiracial, White


<br><br> 

- - -

###  Section-2 Evaluating Missing Values

__§ 2.1__ Which variables have at least one interviewee with a missing (NA) value? (Select all that apply.)

+ PeopleInHousehold
+ Region
+ State
+ MetroAreaCode
+ Age
+ Married
+ Sex
+ Education
+ Race
+ Hispanic
+ CountryOfBirthCode
+ Citizenship
+ EmploymentStatus
+ Industry

```{r}
#直接列出後，目視找出有缺項的變數項目(NA)
summary(CPS)
```
有以下：
MetroAreaCode
Married,Education
EmploymentStatus
Industry


__§ 2.2__  Which is the most accurate:

x The Married variable being missing is related to the Region value for the interviewee.
x The Married variable being missing is related to the Sex value for the interviewee.
O The Married variable being missing is related to the Age value for the interviewee. 
x The Married variable being missing is related to the Citizenship value for the interviewee.
+ The Married variable being missing is not related to the Region, Sex, Age, or Citizenship value for the interviewee.

```{r}
#以表格分別列出後，檢視其關連性
table(CPS$Region, is.na(CPS$Married))
table(CPS$Sex, is.na(CPS$Married))
table(CPS$Age, is.na(CPS$Married))
table(CPS$Citizenship, is.na(CPS$Married))
```
Age


__§ 2.3__ How many states had all interviewees living in a non-metropolitan area (aka they have a missing MetroAreaCode value)? For this question, treat the District of Columbia as a state (even though it is not technically a state).
```{r}
#以表格列出各州不是住在大都會區的人數
table(is.na(CPS$MetroAreaCode),CPS$State)
```
有2州 (Alaska & Wyoming)


How many states had all interviewees living in a metropolitan area? Again, treat the District of Columbia as a state.
```{r}
#以表格列出各州不是住在大都會區的人數
table(is.na(CPS$MetroAreaCode),CPS$State)
```
有3州 
District of Columbia, 
New Jersey, 
Rhode Island


__§ 2.4__ Which region of the United States has the largest proportion of interviewees living in a non-metropolitan area?
```{r}
#以表格列出在美國並非住在大都會區的面試者數量
table(CPS$Region,is.na(CPS$MetroAreaCode))
```
以Midwest為最多 (共10674)


__§ 2.5__ Which state has a proportion of interviewees living in a non-metropolitan area closest to 30%?
```{r}
#選出美國各州中並非住在大都會地區的居民比例，然後排序
tapply(is.na(CPS$MetroAreaCode),CPS$State,mean)%>%sort
```
威斯康辛州最接近30% (為0.29933)


Which state has the largest proportion of non-metropolitan interviewees, ignoring states where all interviewees were non-metropolitan?
```{r}
##選出美國各州中並非住在大都會地區的居民比例並排序，但要剔除極端值(100％)
tapply(is.na(CPS$MetroAreaCode),CPS$State,mean)%>%sort
```
蒙大拿州勝出 Montana （共0.83608）


<br><br> 

- - -

###  Section-3 Integrating Metropolitan Area Data

__§ 3.1__ How many observations (codes for metropolitan areas) are there in MetroAreaMap?
```{r}
#先讀取MetroAreaMap以及CountryMap兩個資料庫，再檢視MetroAreaMap的資料組成
MetroAreaMap=read.csv("data/MetroAreaCodes.csv")
CountryMap=read.csv("data/CountryCodes.csv")
str(MetroAreaMap)
```
共271個觀察值


How many observations (codes for countries) are there in CountryMap?
```{r}
#檢視MountryMap的資料組成
str(CountryMap)
```
共149個觀察值

__§ 3.2__ What is the name of the variable that was added to the data frame by the merge() operation?
```{r}
#先將新項目整合到原資料庫中，再檢視資料組成
CPS = merge(CPS, MetroAreaMap, by.x="MetroAreaCode", by.y="Code", all.x=TRUE)
str(CPS)
```
新增項目為MetroArea

How many interviewees have a missing value for the new metropolitan area variable?
```{r}
#列出各項並檢視有缺漏值的變數項目
summary(CPS)
```
NA's=34238

__§ 3.3__ Which of the following metropolitan areas has the largest number of interviewees?
```{r}
#列出居住在各大都會地區的受面試者數量並由小排到大並選出最後10個
tail(sort(table(CPS$MetroArea)),10)
```
Boston-Cambridge-Quincy, MA-NH

__§ 3.4__ Which metropolitan area has the highest proportion of interviewees of Hispanic ethnicity?
```{r}
#根據條件算出比率後由小排到大並選出最後10個
sort(tapply(CPS$Hispanic, CPS$MetroArea, mean))%>%tail(10)
```
Laredo, TX (0.966292)

__§ 3.5__ Determine the number of metropolitan areas in the United States from which at least 20% of interviewees are Asian.
```{r}
#根據條件選出後，由小到大排序並選出最後10個
tail(sort(tapply(CPS$Race == "Asian", CPS$MetroArea, mean)),10)

```
Honolulu, HI; 
San Francisco-Oakland-Fremont, CA; 
San Jose-Sunnyvale-Santa Clara, CA; 
and Vallejo-Fairfield, CA


__§ 3.6__  Passing na.rm=TRUE to the tapply function, determine which metropolitan area has the smallest proportion of interviewees who have received no high school diploma.
```{r}
#根據條件選出後，由小到大排序並選出前10個
sort(tapply(CPS$Education == "No high school diploma", CPS$MetroArea, mean, na.rm=TRUE))%>%head
```
Iowa City 2.9%

<br><br> 

- - -

###  Section-4 Integrating Country of Birth Data

__§ 4.1__ What is the name of the variable added to the CPS data frame by this merge operation?
```{r}
#合併CPS中的CountryOfBirthCode欄和CountryMap中的Code欄，保留前者的全部欄位，並檢視資料
CPS = merge(CPS, CountryMap, by.x="CountryOfBirthCode", by.y="Code", all.x=TRUE)
summary(CPS)
```
country


How many interviewees have a missing value for the new metropolitan area variable?
```{r}
#檢視新欄位中的缺漏值
summary(CPS)
```
country's NA's =176


__§ 4.2__ Among all interviewees born outside of North America, which country was the most common place of birth?
```{r}
#用表格列出後由小到大排序並取最後10個國家
sort(table(CPS$Country))%>%tail(10)
```
Philippines 839 是美洲外最多的國家


__§ 4.3__ What proportion of the interviewees from the "New York-Northern New Jersey-Long Island, NY-NJ-PA" metropolitan area have a country of birth that is not the United States? 
```{r}
#由MetroArea欄位中只選出上述大都會地區的受面試者數據，再進行比率計算
table(CPS$MetroArea == "New York-Northern New Jersey-Long Island, NY-NJ-PA", CPS$Country != "United States")

1668/(1668+3736)
```
0.3087


__§ 4.4__ Which metropolitan area has the largest number (note -- not proportion) of interviewees with a country of birth in India? 
```{r}
#根據題目條件選出並由小到大排序，再選出最後10筆資料
tapply(CPS$Country=="India",CPS$MetroArea,sum,na.rm=TRUE)%>%sort%>%tail(10)
```
New York


In Brazil?
```{r}
#根據題目條件選出並由小到大排序，再選出最後10筆資料
tapply(CPS$Country=="Brazil",CPS$MetroArea,sum,na.rm=TRUE)%>%sort%>%tail(10)
```
Boston

In Somalia?
```{r}
#根據題目條件選出並由小到大排序，再選出最後10筆資料
sort(tapply(CPS$Country == "Somalia", CPS$MetroArea, sum, na.rm=TRUE))%>%tail(10)
```
Minneapolis


<br><br><br>
