---
title: "AS3-2: 股市動態"
author: "第 6 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

組員： `B035040052 林榮鏵` `B056090039 楊禾馨` `M064020056閻俞蓉` `M064111003 洪筱涵` `M074111035 劉志峰`

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

**股票動態**

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>

###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
#讀取五個檔案
IBM=read.csv("data/IBMStock.csv")
GE=read.csv("data/GEStock.csv")
ProcterGamble=read.csv("data/ProcterGambleStock.csv")
CocaCola=read.csv("data/CocaColaStock.csv")
Boeing=read.csv("data/BoeingStock.csv")
#計算number of row
nrow(IBM)
```
480 observations

__§ 1.2__ What is the earliest year in our datasets?
```{r}
#先將Date欄位屬性從factor轉成date
IBM$Date = as.Date(IBM$Date, "%m/%d/%y")
GE$Date = as.Date(GE$Date, "%m/%d/%y")
CocaCola$Date = as.Date(CocaCola$Date, "%m/%d/%y")
ProcterGamble$Date = as.Date(ProcterGamble$Date, "%m/%d/%y")
Boeing$Date = as.Date(Boeing$Date, "%m/%d/%y")
#找出最早的年份
IBM$Date[which.min(IBM$Date)]
#另一種寫法
min(IBM$Date) 
```
1970

__§ 1.3__ What is the latest year in our datasets?
```{r}
#找出最晚的年份
IBM$Date[which.max(IBM$Date)]
```
2009

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
#IBM的平均股價
mean(IBM$StockPrice) #144.4
```
mean:144.4

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
#GE的股價最小值
min(GE$StockPrice) #9.294
```
min:9.294

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
#Coca Cola的股價最大值
max(CocaCola$StockPrice) #146.6
```
max:146.6

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
#Boeing的股價中位數
median(Boeing$StockPrice) #44.88
```
median:44.88

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
#Procter & Gamble的股價標準差
sd(ProcterGamble$StockPrice) #18.19
```
sd:18.19

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
#X軸為年份，y軸為股價
plot(CocaCola$Date,CocaCola$StockPrice,type="l")
```
<br>highest year: 1973, lowest year: 1980

__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
#Coca cola為紅色線
plot(CocaCola$Date,CocaCola$StockPrice,type="l",col="red")
#Procter & Gamble為藍色線
lines(ProcterGamble$Date, ProcterGamble$StockPrice,col="blue")
#在2000年三月加一條綠色虛線
abline(v=as.Date(c("2000-03-01")), lwd=2, lty=2, col="green")
```
<br>ProcterGamble (藍色線) dropped more.

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
#Coca cola為紅色線
plot(CocaCola$Date,CocaCola$StockPrice,type="l",col="red")
#Procter & Gamble為藍色線
lines(ProcterGamble$Date, ProcterGamble$StockPrice,col="blue")
#在1983年加一條綠色虛線
abline(v=as.Date(c("1983-01-01")), lwd=2, lty=2,col="green")
```
<br>Coca Cola (紅色線) 的股價上升

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
# same as the plot above
```
<br>Coca-Cola has lower values

<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
which(CocaCola$Date=="1995-01-01") #1995年從301row開始
which(CocaCola$Date=="2005-12-01") #2005年到第432row結束
plot(CocaCola$Date[301:432], CocaCola$StockPrice[301:432], type="l", col="red", ylim=c(0,210))
lines(ProcterGamble$Date[301:432], ProcterGamble$StockPrice[301:432],col="blue", ylim=c(0,210))
lines(IBM$Date[301:432], IBM$StockPrice[301:432],col="green", ylim=c(0,210))
lines(GE$Date[301:432], GE$StockPrice[301:432],col="purple", ylim=c(0,210))
lines(Boeing$Date[301:432], Boeing$StockPrice[301:432],col="orange", ylim=c(0,210))
#在2000年三月加上一條灰色虛線
abline(v=as.Date(c("2000-03-01")), lwd=2, col="gray",lty=2)
#GE:pruple
#col = "red", "blue", "green", "purple", "orange", and "black"
#lty = 2:dashed, 3:dotted, 4:alternate between dashes and dots, 5:long-dashed
```
<br>GE fell the most.

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
# see the graph above
#green:IBM
```
<br>IBM reaches the highest value.

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
plot(CocaCola$Date[301:372], CocaCola$StockPrice[301:372], type="l", col="red", ylim=c(0,210))
lines(ProcterGamble$Date[301:372], ProcterGamble$StockPrice[301:372],col="blue", ylim=c(0,210))
lines(IBM$Date[301:372], IBM$StockPrice[301:372],col="green", ylim=c(0,210))
lines(GE$Date[301:372], GE$StockPrice[301:372],col="purple", ylim=c(0,210))
lines(Boeing$Date[301:372], Boeing$StockPrice[301:372],col="orange", ylim=c(0,210))
#在1997九月到1997十一月加上虛線
abline(v=as.Date(c("1997-09-01")), lwd=1, lty=2)
abline(v=as.Date(c("1997-11-01")), lwd=1, lty=2)
# blue:ProcterGamble, orange:Boeing
```
<br>ProcterGamble and Boeing decreased trend in their stock price.

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
plot(CocaCola$Date[301:432], CocaCola$StockPrice[301:432], type="l", col="red", ylim=c(0,210))
lines(ProcterGamble$Date[301:432], ProcterGamble$StockPrice[301:432],col="blue", ylim=c(0,210))
lines(IBM$Date[301:432], IBM$StockPrice[301:432],col="green", ylim=c(0,210))
lines(GE$Date[301:432], GE$StockPrice[301:432],col="purple", ylim=c(0,210))
lines(Boeing$Date[301:432], Boeing$StockPrice[301:432],col="orange", ylim=c(0,210))
##在2004年和2005年加上線
abline(v=as.Date(c("2004-01-01")), lwd=2)
abline(v=as.Date(c("2005-01-01")), lwd=2)
#orange:Boeing
```
<br>Boeing increased stock price.

<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
tapply(IBM$StockPrice,months(IBM$Date),mean) %>%sort
mean(IBM$StockPrice) # 144.4
#January<May<April<March<February 
```
<br>February, March, April, May, January have higher stock price than average(144.4).

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
tapply(GE$StockPrice,months(GE$Date),mean) %>%sort
tapply(CocaCola$StockPrice,months(CocaCola$Date),mean) %>%sort
#April
```
<br>General Electric and Coca-Cola both have their highest average stock price in April.

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
tapply(GE$StockPrice,months(GE$Date),mean) %>%sort
```
<br>The stock prices are lower in December.

<br><br><br>

