---
title: "AS3-2: 股市動態"
author: "第 0 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

**股票動態**

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>

###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
IBM=read.csv('data/IBMStock.csv')
GE=read.csv('data/GEStock.csv')
ProcterGamble=read.csv('data/ProcterGambleStock.csv')
CocaCola=read.csv('data/CocaColaStock.csv')
Boeing=read.csv('data/BoeingStock.csv')

IBM$Date=as.Date(IBM$Date,"%m/%d/%y")
GE$Date=as.Date(GE$Date,"%m/%d/%y")
ProcterGamble$Date=as.Date(ProcterGamble$Date,"%m/%d/%y")
CocaCola$Date=as.Date(CocaCola$Date,"%m/%d/%y")
Boeing$Date=as.Date(Boeing$Date,"%m/%d/%y")
#
#
```


__§ 1.2__ What is the earliest year in our datasets?
```{r}
IBM$Date[which.min(IBM$Date)]
min(IBM$Date)#也是可以
#
#
```

__§ 1.3__ What is the latest year in our datasets?
```{r}
max(IBM$Date)
#
#
```

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
mean(IBM$StockPrice)
#
#
```

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
min(GE$StockPrice)
#
#
```

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
max(CocaCola$StockPrice)
#
#
```

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
median(Boeing$StockPrice)
#
#
```

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
sd(ProcterGamble$StockPrice)
#
#
```

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
plot(CocaCola$Date,CocaCola$StockPrice,type="l")

#
#
```


__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
plot(CocaCola$Date,CocaCola$StockPrice,type="l",col="red")
lines(ProcterGamble$Date,ProcterGamble$StockPrice,col="blue",lty=2)
abline(v=as.Date(c("2000-03-01")),lwd=2)
#
#
```

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
plot(CocaCola$Date,CocaCola$StockPrice,type="l",col="red")
lines(ProcterGamble$Date,ProcterGamble$StockPrice,col="blue",lty=2)
abline(v=as.Date(c("1983-01-01")),lwd=2)
#程式碼 下 zoom
#
```

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
plot(CocaCola$Date,CocaCola$StockPrice,type="l",col="red")
lines(ProcterGamble$Date,ProcterGamble$StockPrice,col="blue",lty=2)
abline(v=as.Date(c("1983-01-01")),lwd=2)
#cocacola red point
#
```


<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
plot(CocaCola$Date,CocaCola$StockPrice,type="l",col="red")
lines(ProcterGamble$Date,ProcterGamble$StockPrice,col="blue",lty=1)
lines(Boeing$Date,Boeing$StockPrice,col="yellow",lty=1)
lines(GE$Date,GE$StockPrice,col="green",lty=1)
lines(IBM$Date,IBM$StockPrice,col="purple",lty=1)
abline(v=as.Date(c("2000-03-01")),lwd=2)
#
#
```

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
which(CocaCola$Date=="1995-01-01")
which(CocaCola$Date=="2005-12-01")
plot(CocaCola$Date[301:432],CocaCola$StockPrice[301:432],type="l",col="red",ylim = c(0,210))
lines(ProcterGamble$Date[301:432],ProcterGamble$StockPrice[301:432],col="blue",lty=1,ylim = c(0,210))
lines(Boeing$Date[301:432],Boeing$StockPrice[301:432],col="yellow",lty=1,ylim = c(0,210))
lines(GE$Date[301:432],GE$StockPrice[301:432],col="green",lty=1,ylim = c(0,210))
lines(IBM$Date[301:432],IBM$StockPrice[301:432],col="purple",lty=1,ylim = c(0,210))
abline(v=as.Date(c("2000-03-01")),lwd=2)
#lty=2,3,4,5
#col=red,blue,green,purple,black,orange,yellow
#ylim= 是y軸範圍的控制
#ans=GE
#ans=IBM
```

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
which(CocaCola$Date=="1997-09-01")
which(CocaCola$Date=="1997-11-01")
plot(CocaCola$Date[333:335],CocaCola$StockPrice[333:335],type="l",col="red",ylim = c(45,120))
lines(ProcterGamble$Date[333:335],ProcterGamble$StockPrice[333:335],col="blue",lty=1,ylim = c(45,120))
lines(Boeing$Date[333:335],Boeing$StockPrice[333:335],col="yellow",lty=1,ylim = c(45,120))
lines(GE$Date[333:335],GE$StockPrice[333:335],col="green",lty=1,ylim = c(45,120))
lines(IBM$Date[333:335],IBM$StockPrice[333:335],col="purple",lty=1,ylim = c(45,120))
abline(v=as.Date(c("1997-10-01")),lwd=2)
#blue=ProcterGamble
#yellow=Boeing
```

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
which(CocaCola$Date=="1995-01-01")
which(CocaCola$Date=="2005-12-01")
plot(CocaCola$Date[301:432],CocaCola$StockPrice[301:432],type="l",col="red",ylim = c(0,210))
lines(ProcterGamble$Date[301:432],ProcterGamble$StockPrice[301:432],col="blue",lty=1,ylim = c(0,210))
lines(Boeing$Date[301:432],Boeing$StockPrice[301:432],col="yellow",lty=1,ylim = c(0,210))
lines(GE$Date[301:432],GE$StockPrice[301:432],col="green",lty=1,ylim = c(0,210))
lines(IBM$Date[301:432],IBM$StockPrice[301:432],col="purple",lty=1,ylim = c(0,210))
abline(v=as.Date(c("2004-01-01")),lwd=2)
abline(v=as.Date(c("2005-01-01")),lwd=2)
#ans=Boieng

```


<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
tapply(IBM$StockPrice,months(IBM$Date),mean)%>%sort
mean(IBM$StockPrice)

#sort做順序
# use 大於
```

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
tapply(GE$StockPrice,months(GE$Date),mean)%>%sort
tapply(CocaCola$StockPrice,months(CocaCola$Date),mean)%>%sort

#
#
```

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
tapply(GE$StockPrice,months(GE$Date),mean)%>%sort
tapply(CocaCola$StockPrice,months(CocaCola$Date),mean)%>%sort
tapply(IBM$StockPrice,months(IBM$Date),mean)%>%sort
tapply(ProcterGamble$StockPrice,months(ProcterGamble$Date),mean)%>%sort
tapply(Boeing$StockPrice,months(Boeing$Date),mean)%>%sort
#
#
```

<br><br><br>

