---
title: "AS3-1: 數位偵探"
<<<<<<< HEAD
author: "第 6 組"
=======
author: "第 0 組"
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=F}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr, d3heatmap)
```
<hr>

犯罪是一個國際關注的問題，但它在不同的國家以不同的方式記錄和處理。 在美國，聯邦調查局（FBI）記錄了暴力犯罪和財產犯罪。 此外，每個城市都記錄了犯罪行為，一些城市發布了有關犯罪率的數據。 伊利諾伊州芝加哥市從2001年開始在線發布犯罪數據。

芝加哥是美國人口第三多的城市，人口超過270萬。在這個作業裡面，我們將關注一種特定類型的財產犯罪，稱為「汽車盜竊」，我們將使用R中的一些基本數據分析來了解芝加哥的汽車盜竊紀錄。請載入文件"data/mvtWeek1.csv"：以下是各欄位的描述：

+ `ID`: a unique identifier for each observation
+ `Date`: the date the crime occurred
+ `LocationDescription`: the location where the crime occurred
+ `Arrest`: whether or not an arrest was made for the crime (TRUE if an arrest was made, and FALSE if an arrest was not made)
+ `Domestic`: whether or not the crime was a domestic crime, meaning that it was committed against a family member (TRUE if it was domestic, and FALSE if it was not domestic)
+ `Beat`: the area, or "beat" in which the crime occurred. This is the smallest regional division defined by the Chicago police department.
+ `District`: the police district in which the crime occured. Each district is composed of many beats, and are defined by the Chicago Police Department.
+ `CommunityArea`: the community area in which the crime occurred. Since the 1920s, Chicago has been divided into what are called "community areas", of which there are now 77. The community areas were devised in an attempt to create socially homogeneous regions.
+ `Year`: the year in which the crime occurred.
+ `Latitude`: the latitude of the location at which the crime occurred.
+ `Longitude`: the longitude of the location at which the crime occurred.

<br>

- - -

###  Section-1 Loading the Data

【1.1】How many rows of data (observations) are in this dataset?
```{r}
<<<<<<< HEAD
mvt = read.csv("data/mvtWeek1.csv", stringsAsFactors=F)
nrow(mvt)
```
191641 rows

檢查各欄位的資料格式
```{r}
summary(mvt)
=======
WHO=read.csv("data/mvtWeek1.csv")
#
```

檢查各欄位的資料格式
```{r}
ncol(WHO)
#ncol = 欄位

nrow(WHO)
#nrow = 記錄

summary(WHO)
#資料總覽
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

類別(Factor) versus 字串(Character)

【1.2】How many variables are in this dataset?
```{r}
<<<<<<< HEAD
ncol(mvt)
=======
ncol(WHO)
#多少變數欄位？（物件）
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```


【1.3】Using the "max" function, what is the maximum value of the variable "ID"?
```{r}
<<<<<<< HEAD
max(mvt$ID)
=======
which.max(WHO$ID)
#找出ID變數的最大值為何
WHO[18134,]
#顯示記錄18134（位置） 的所有變數資料（物件）
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```


【1.4】 What is the minimum value of the variable "Beat"?
```{r}
<<<<<<< HEAD
min(mvt$Beat)
=======
which.min(WHO$Beat)
#顯示記錄位置
WHO[4756,]
#透過記錄位置找出資料
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```


【1.5】 How many observations have value TRUE in the Arrest variable (this is the number of crimes for which an arrest was made)?
```{r}
<<<<<<< HEAD
summary(mvt)
sum(mvt$Arrest)
#mean(mvt$Arrest)
=======
table(WHO$Arrest)
#使用table做分類計算
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

【1.6】 How many observations have a LocationDescription value of ALLEY?
```{r}
<<<<<<< HEAD
sum(mvt$LocationDescription == "ALLEY")
=======
table(WHO$LocationDescription =="ALLEY")
#利用==""搜索名稱
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```


<br><br>

- - -

### Section-2 Understanding Dates in R

【2.1】 In what format are the entries in the variable Date?

<<<<<<< HEAD
Month/Day/Year Hour:Minute

```{r}
head(mvt$Date)  # Month/Day/Year Hour:Minute
mvt$Date[1]
```

```{r}
ts = as.POSIXct(mvt$Date, format="%m/%d/%y %H:%M")
par(cex=0.7)
hist(ts,"year",las=2,freq=T,xlab="")
```

```{r}
table(format(ts,'%w'))
table(format(ts,'%m'))
table(weekday=format(ts,'%w'), month=format(ts,'%m'))
```

```{r fig.height=2.5, fig.width=8}
library(dplyr)
library(d3heatmap)
table(format(ts,"%u"), format(ts,"%H")) %>% 
  as.data.frame.matrix %>% 
  d3heatmap(F,F,col=colorRamp(c('seagreen','lightyellow','red')))
=======
+ Month/Day/Year Hour:Minute
+ Day/Month/Year Hour:Minute
+ Hour:Minute Month/Day/Year
+ Hour:Minute Day/Month/Year

```{r}
head(WHO$Date)
#顯示資料框中的時間
```

```{r}
ts=as.POSIXct(WHO$Date,format="%m/%d/%y %H:%M")
#as.Date(strptime(WHO$Date,"%m/%d/%y %H:%M"))
#先建立一個新的時間物件，把原檔的時間存入新物件

```

```{r}
table(format(ts,"%u"))
table(format(ts,"%m"))
table(weekday=format(ts,"%u"),month=format(ts,"%m"))
#透過table將ts的format更改為我們想要的格式
```

```{r fig.height=2.5, fig.width=8}
table(format(ts,"%u"), format(ts,"%H")) %>% 
  as.data.frame.matrix %>% 
  d3heatmap(F,F,col=colorRamp(c('seagreen','lightyellow','red')))

table(format(ts,"%u"), format(ts,"%H")) %>% 
  as.data.frame.matrix %>% 
  d3heatmap(T,T,col=colorRamp(c('seagreen','lightyellow','red')))

table(format(ts,"%u"), format(ts,"%H")) %>% 
  as.data.frame.matrix %>% 
  d3heatmap(T,F,col=colorRamp(c('seagreen','lightyellow','red')))

table(format(ts,"%u"), format(ts,"%H")) %>% 
  as.data.frame.matrix %>% 
  d3heatmap(F,T,col=colorRamp(c('seagreen','lightyellow','red')))

>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```


【2.2】 What is the month and year of the median date in our dataset? 
```{r}
<<<<<<< HEAD
DateConvert = as.Date(strptime(mvt$Date, "%m/%d/%y %H:%M"))
# ts = as.POSIXct(mvt$Date, format="%m/%d/%y %H:%M")
summary(DateConvert)
median(DateConvert)
=======
summary(ts)
median(ts)
#
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

【2.3】 In which month did the fewest motor vehicle thefts occur?
```{r}
<<<<<<< HEAD
mvt$Month = months(DateConvert)
mvt$Weekday = weekdays(DateConvert)
mvt$Date = DateConvert
sort(table(mvt$Month))
=======
sort(table(format(ts,"%m")))
#月份去排序（少到多），哪個犯罪率最高
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

【2.4】 On which weekday did the most motor vehicle thefts occur?
```{r}
<<<<<<< HEAD
sort(table(mvt$Weekday))
=======

max(table(format(ts,"%w")))
#星期中的最大值是多少？

which.max(table(format(ts,"%w")))
#最大值的星期為何？（%w：5，6 因為order與sort的緣故， %u：5，5）
#因此which.max會先呈現出sort，之後才是order

table(format(ts,"%w"))%>%order
#order只會顯示最大值的位置排名順序

table(format(ts,"%w"))%>%sort
#而sort則連同排名位置及記錄一同顯現



>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

【2.5】 Which month has the largest number of motor vehicle thefts for which an arrest was made?
```{r}
<<<<<<< HEAD
table(mvt$Arrest,mvt$Month)
=======
table(WHO$Arrest)
table(format(ts[WHO$Arrest],"%m"))%>%sort

#我知道被捉的資料可是要如何得知其中哪個月捉得最多的呢？
#若要得知這份資料
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

<br><br>

- - -

### Section-3 Visualizing Crime Trends

【3.1】 (a) In general, does it look like crime increases or decreases from 2002 - 2012? (b) In general, does it look like crime increases or decreases from 2005 - 2008? (c) In general, does it look like crime increases or decreases from 2009 - 2011?
```{r}
<<<<<<< HEAD
hist(ts,'year',las=2)
# 2002~2012 : decrease
# 2005~2008 : decrease
# 2009~2011 : increase
hist(mvt$Date, breaks=100)
=======
hist(ts,'year',las=0)
hist(ts,'year',las=1)
hist(ts,'year',las=2)
hist(ts,'year',las=3)
#2002 - 2012 = decrease
#2005 - 2008 = decrease
#2009 - 2011 = increase
#las 的差別在於x與y軸的變數名稱是否垂直於坐標軸又或是平行於坐標軸（主要是會影響我們觀察數據：一般會使用2(y:直,x:直)）
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

【3.2】 Does it look like there were more crimes for which arrests were made in the first half of the time period or the second half of the time period?
```{r}
<<<<<<< HEAD
table(ts > as.POSIXct("2007-01-01"))
# first half
boxplot(mvt$Date ~ mvt$Arrest)
```
Arrest=TRUE is definitely skewed towards the bottom of the plot, meaning that there were more crimes for which arrests were made in the first half of the time period.

【3.3】 For what proportion of motor vehicle thefts in 2001 was an arrest made?
```{r}
round(prop.table(table(mvt$Arrest, mvt$Year),2),3)
=======
hist(ts[WHO$Arrest],'year',las=2)
#ans = first half of the time period

```

【3.3】 For what proportion of motor vehicle thefts in 2001 was an arrest made?
```{r}
table(WHO$Arrest, format(ts,'%Y')) %>% prop.table(2) %>% round(3) # 0.104
round(prop.table(table(WHO$Arrest,format(ts,'%Y')),margin=2),digits=3) 
#以上兩者皆可，利用管線可能會更簡便一些！
#prop.table是比例的計算 分別是(2)是每個『欄』的計算（年比例），而(1)則是每個『列』的計算（逮捕效率）
#round則是小數點幾位數
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

【3.4】 For what proportion of motor vehicle thefts in 2007 was an arrest made?
```{r}
<<<<<<< HEAD
round(prop.table(table(mvt$Arrest, mvt$Year),2),3)
=======
#查看3.3表
#0.085
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

【3.5】 For what proportion of motor vehicle thefts in 2012 was an arrest made?
```{r}
<<<<<<< HEAD
round(prop.table(table(mvt$Arrest, mvt$Year),2),3)
=======
#查看3.3表
#0.039
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

<br><br>

- - -

### Section-4 Popular Locations

【4.1】 Which locations are the top five locations for motor vehicle thefts, excluding the "Other" category? You should select 5 of the following options.

```{r}
<<<<<<< HEAD
sort(table(mvt$LocationDescription)) %>% tail()
=======
table(WHO$LocationDescription)%>%sort%>%tail(6)

#先是整理再將尾數捉出來

>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

【4.2】 How many observations are in Top5?
```{r}
<<<<<<< HEAD
#1
Top5 = subset(mvt, LocationDescription=="STREET" | LocationDescription=="PARKING LOT/GARAGE(NON.RESID.)" | LocationDescription=="ALLEY" | LocationDescription=="GAS STATION" | LocationDescription=="DRIVEWAY - RESIDENTIAL")
str(Top5)
#2
TopLocations = c("STREET", "PARKING LOT/GARAGE(NON.RESID.)", "ALLEY", "GAS STATION", "DRIVEWAY - RESIDENTIAL")
Top5 = subset(mvt, LocationDescription %in% TopLocations)
=======
(top5=names(table(WHO$LocationDescription)%>%sort%>%tail(6))[-4])
sum((WHO$LocationDescription)%in%top5)

#外加()可以直接顯示計算結果，names=只列出名字，[-4]刪去第四項（注意負號要放在中括號裡頭）
#%in% 前者的運算通過後者的架構輸出答案
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

【4.3】 One of the locations has a much higher arrest rate than the other locations. Which is it? 
```{r}
<<<<<<< HEAD
Top5$LocationDescription = factor(Top5$LocationDescription)
prop.table(table(Top5$LocationDescription,Top5$Arrest),1)
=======
TOP5 = subset(WHO, LocationDescription %in% top5)
tapply(TOP5$Arrest, TOP5$LocationDescription, mean) %>% sort
#
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

【4.4】 On which day of the week do the most motor vehicle thefts at gas stations happen?
```{r}
<<<<<<< HEAD
table(Top5$LocationDescription, Top5$Weekday)
=======
ts[WHO$Location == "GAS STATION"] %>% format('%w') %>% table %>% sort
#
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```

【4.5】 On which day of the week do the fewest motor vehicle thefts in residential driveways happen?
```{r}
<<<<<<< HEAD
table(Top5$LocationDescription, Top5$Weekday)
=======
ts[WHO$Location == "DRIVEWAY - RESIDENTIAL"] %>% 
  format('%w') %>% table %>% sort
#
>>>>>>> 29cb088a8bb7ef96191f373d87d43a8f8c70e434
```


<br><br><br>


